Tickle me BERT: Using laughter to probe pre-trained encoders for dialogue act recoginiton

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
add appendix figure

The pre-trained model is more accurate than the randomly initialized model by several percentage points on both DA corpora,
suggesting that BERT's extensive pre-training does provide some useful information for recoginizing different dialogue acts (Table~\ref{table:exp2}).
This performance boost is much more pronounced in the macro-averaged F1 score,
which is explained by the fact that at the tag level, pre-training has a larger impact on less frequent tags.

@@

\bibliography{acl2020}
\bibliographystyle{acl_natbib}
\clearpage
\appendix
\begin{figure*}[h!]
  \section{Supplementary materials}\label{sec:suppl}
  \centering
  \includegraphics[width=\linewidth]{img/SWDA-bertLvsNL.pdf}
  \includegraphics[width=\linewidth]{img/AMI-DA-bertLvsNL.pdf}
  \caption{Change in accuracy for each dialogue act (\texttt{BERT-NL} vs \texttt{BERT-L}). Positive changes when adding laughter (\texttt{BERT-L}) are shown in blue. Vertical bars indicate how often dialogue act is associated with laughter. Top chart: SWDA, Bottom chart: AMI-DA. }
    \label{fig:by-da}
  \end{figure*}

>>>>

The pre-trained model is more accurate than the randomly initialized model by several percentage points on both DA corpora,
suggesting that BERT's extensive pre-training does provide some useful information for recoginizing different dialogue acts (Table~\ref{table:exp2}).
This performance boost is much more pronounced in the macro-averaged F1 score,
which is explained by the fact that at the tag level, pre-training has a larger impact on less frequent tags.
For a disaggregeated view, see Figure \ref{fig:f1-by-da} in Appendix~\ref{sec:suppl} p

@@

\bibliography{acl2020}
\bibliographystyle{acl_natbib}
\clearpage
\appendix

\begin{figure*}[h!]
\section{Supplementary materials}\label{sec:suppl}
  \centering
  \includegraphics[width=\linewidth]{img/SWDA-bertLvsNL.pdf}
  \includegraphics[width=\linewidth]{img/AMI-DA-bertLvsNL.pdf}
  \caption{Change in accuracy for each dialogue act (\texttt{BERT-NL} vs \texttt{BERT-L}). Positive changes when adding laughter (\texttt{BERT-L}) are shown in blue. Vertical bars indicate how often dialogue act is associated with laughter. Top chart: SWDA, Bottom chart: AMI-DA. }
    \label{fig:by-da}
  \end{figure*}

\begin{figure*}[h!]
  \centering
  \includegraphics[width=\linewidth]{img/swda-brf.pdf}
  \includegraphics[width=\linewidth]{img/ami-brf.pdf}
  \caption{F1 scores by dialogue act for BERT with standard pre-training and DAR fine-tuning (\texttt{BERT-FT}) vs.~the same model without pre-training (\texttt{BERT-RI}) and without fine-tuning (\texttt{BERT-FZ}). Dialogue acts are ordered with the most common on the left.
    \label{fig:f1-by-da}
  \end{figure*}
